---
title: "genderwagegap"
author: "Yacine, Victoria and Raphaële"
date: "11/23/2021"
output: 
 github_document: default
---

```{r}
setwd("/Users/hugomarty/Documents/GitHub/Project-of-Econometrics/EE_2018")

install.packages("haven")  
library(haven)
d <- read_dta("~/Documents/GitHub/Project-of-Econometrics/EE_2018/Bases/EEC_2018INDIV.dta")
View(d)

 
d$TempsComplet <- ifelse(d$duhab<4,0,1)
d <- subset(d,TempsComplet==1, drop=TRUE)
library(tidyverse)
dr <- d %>% select(ident,
                  salmee, #salaire continu
                  salmet, #salaire discontinu
                  sexe, #sexe
                  ag, #âge en variable continue
                  nbenfa18, #nombre d'nefants de moins 18
                  dip5, # éducation en 13 postes
                  cser, #CPS
                  nafantg004n, # primaire / secondaire / tertiaire
                  chpub, # public / privé
                  ancentr, # ancienneté 
                  immi, # être immigré
                  desc,#être descendant
                  zus) # zone urbaine sensible


# education, employment, household charecteristics, gender, occupation, industry, age)
# temps complets

```


3) First Table: Provide a table with brief summary statistics.

```{r}

# Sample size

# Average age in the population

# Distribution of education

# Occupation

```


4) Second Table: Perform a regression of log wages on a gender dummy variable without other controls (unconditional wage gap). Perform similar regressions but include progressively additional sets of control variables. Report regression results in a single table across different columns as in an academic paper. Comment the results

```{r}

```


5) Third Table: Perform the same exercise but separately for those with more and less than high-school education

```{r}

```


6) Fourth Table (not compulsory): Perform further analysis that you might find interesting 7) Comment

```{r}

```

